The value of being indispensable: a cooperative approach to bargaining with a continuum of players

### 2024-08-11 src/paper/theory.tex
Add proofs for more general multiple platforms case.

Let us first establish the sum of the shares of all big players.
Then, the value of individual big players can be obtained by relying on the symmetry assumption.
The following proposition provides an expression for the limit of this total value.
\begin{proposition}
    \label{prop:multiple_platforms_total}
    Let $f$ be continuous on [0, 1].
    Let us denote the number of fringe players in any coalition $S$ as $n_F(S)$.
    Furthermore, let us denote the random variable $\frac{n_F(\mathcal{P}_{P_j})}{n}$ as $X_n$.
    Assume that $X_n \xrightarrow[]{d} X$ with cdf $G(t)$ and (if exists) pdf $g(t)$.

    Let $H(t) = 1 - [1 - G(t)]^m$, i.e. the cdf of the minimum of the $m$ independent random variables distributed according to $G$.
    Then
    \begin{align*}
        \varphi_P^\infty = \lim_{n \to \infty} \sum_{j=1}^m \varphi_{P_j}^n = \int_0^1 f(t) \dH(t) = \int_0^1 h(t) f(t) \dt,
    \end{align*}
    with the last equality holding if $X$ is a continuous random variable.
\end{proposition}
% TODO: needs proof

@@

Finally, let us look at how the value of the big players and the fringe changes as a function of the number of the big players.
Proposition \Cref{cor:multiple_platforms_2} again confirms our intuition: more players means that they become more substitutable, and thus their bargaining power decreases.
This not only means that the value of each individual big player decreases, but also that their total value goes down.
\begin{corollary}
    \label{cor:multiple_platforms_2}
    Let $\varphi_{P}^{\infty, m}$ denote the aggregated values of players of type $P$. $\varphi_{P}^{\infty, m}$ is decreasing in $m$ and $\varphi_{A}^{\infty, m}$ is increasing in $m$ unless $f$ is constant.
\end{corollary}
% TODO: adjust proof

@@

Now let us look at how the value of the big players and the fringe changes as a function of the number of the big players.
Proposition \Cref{cor:multiple_platforms_2} again confirms our intuition: more players means that they become more substitutable, and thus their bargaining power decreases.
This not only means that the value of each individual big player decreases, but also that their total value goes down.

\begin{corollary}
    \label{cor:multiple_platforms_2}
    Let $\varphi_{P}^{\infty, m} = m\varphi_{P_i}^{\infty, m}$ denote the aggregated values of players of type $P$. $\varphi_{P}^{\infty, m}$ is decreasing in $m$ and $\varphi_{A}^{\infty, m}$ is increasing in $m$ unless $f$ is constant.
\end{corollary}

Finally, let us show that the value of the fringe has a similar, marginal contribution-based interpretation as in the case of a single big player.

\begin{corollary}
    \label{cor:multiple_platforms}
    The per-unit Shapley-value of the fringe is
    \begin{align*}
        \varphi_A^{\infty, m} = 1 - \int_0^1 f(t) \dG(t) = \int_0^1 G(t) f'(t) \dt ,
    \end{align*}
    where $G(t) = 1 - (1-t)^m$.
\end{corollary}

@@

@@

\begin{proof}[Proof of Corollary \ref{cor:multiple_platforms_2}] (Assuming $f$ is continuously differentiable) %\textcolor{red}{(Assuming $f$ is continuously differentiable -- will have to relax this)}
    $f'(t)$ is non-negative, so $[1 - (1-t)^m] f'(t)$ is increasing in $m$ $\forall t \in [0, 1]$.
    As a consequence, $\varphi_A^{n, \infty}$ is also increasing in $m$ if $f'(t)$ is positive on some interval or, $f(t)$ is not constant.
    Conversely, $\varphi_{P}^{\infty, m} = 1 - \varphi_{A}^{\infty, m}$ is decreasing in $m$.
\end{proof}

>>>>

Let us first establish the sum of the shares of all big players.
Then, the value of individual big players can be obtained by relying on the symmetry assumption.
The following proposition provides an expression for the limit of this total value.
\begin{proposition}
    \label{prop:multiple_platforms_total}
    Let $f$ be continuous on [0, 1].
    Let us denote the number of fringe players in any coalition $S$ as $n_A(S)$.
    Furthermore, let us denote the random variable $\frac{n_A(\mathcal{P}_{P_j})}{n}$ as $X_n^j$.
    Assume that $X_n^j$ and $X_n^k$ are independent for all $j \neq k$.
    Furthermore, supppose that $X_n^j \xrightarrow[]{d} X^j$ with cdf $G(t)$ and (if exists) pdf $g(t)$ for every $j = 1, \dots, m$.

    Let $H(t) = 1 - [1 - G(t)]^m$, i.e. the cdf of the minimum of the $m$ independent random variables distributed according to $G$.
    Then
    \begin{align*}
        \varphi_P^\infty = \lim_{n \to \infty} \sum_{j=1}^m \varphi_{P_j}^n = \int_0^1 f(t) \dH(t) = \int_0^1 h(t) f(t) \dt,
    \end{align*}
    with the last equality holding if $X$ is a continuous random variable.
\end{proposition}

@@

Finally, let us look at how the value of the big players and the fringe changes as a function of the number of the big players.
Proposition \Cref{cor:multiple_platforms_2} again confirms our intuition: more players means that they become more substitutable, and thus their bargaining power decreases.
This not only means that the value of each individual big player decreases, but also that their total value goes down.
\begin{corollary}
    \label{cor:multiple_platforms_2}
    Let $\varphi_{P}^{\infty, m}$ denote the aggregated values of players of type $P$. $\varphi_{P}^{\infty, m}$ is decreasing in $m$ and $\varphi_{A}^{\infty, m}$ is increasing in $m$ unless $f$ is constant or $X$ is degenerate.
\end{corollary}
% TODO: adjust proof

@@

@@

\begin{proof}[Proof of \Cref{prop:multiple_platforms_total}]
    Observe that, in any order, only the first big player has a positive marginal contribution.
    Therefore, given $n$ fringe firms, the total value generated by the big players is
    \begin{align*}
        \varphi^{n, m}_P &= \sum_{j=1}^m \sum_R \Pr(R) [ v(\mathcal{P}^R_{P_j} \cup \{i\}) - v(\mathcal{P}^R_{P_j}) ] \\
        &= \sum_{j=1}^m \sum_{k=0}^n \Pr(n_A(\mathcal{P}^R_{P_j}) = k \land n_P(\mathcal{P}^R_{P_j}) = 0) f(k/n),
    \end{align*}
    where $n_A(S)$ and $n_P(S)$ denote the number of fringe players and big players in coalition $S$, respectively.
    This can be further rewritten as
    \begin{align*}
        \varphi^{n, m}_P &= \sum_{j=1}^m \sum_{k=0}^n \Pr(n_A(\mathcal{P}^R_{P_j}) = k \mid n_P(\mathcal{P}^R_{P_j}) = 0) \Pr(n_P(\mathcal{P}^R_{P_j}) = 0) f(k/n) \\
        &= \sum_{k=0}^n \Pr(n_A(\mathcal{P}^R_{P_j}) = k \mid n_P(\mathcal{P}^R_{P_j}) = 0) f(k/n),
    \end{align*}
    where the last equality follows from the fact that the big players are identical in terms of permutation probabilities.

    Remember that the share of fringe players before player $j$ is described by the random variable $X_n^j = n_A(\mathcal{P}^R_{P_j}) / n$.
    Observe that
    \begin{align*}
        \Pr(X_n^j = k/n \mid n_P(\mathcal{P}^R_{P_j}) = 0) &= \Pr(X_n^j = k/n \mid X_n^j = \min\{X_n^1, \dots, X_n^m\} \land n_P(\mathcal{P}^R_{P_j}) = 0) \\
        &= \Pr(\min\{X_n^1, \dots, X_n^m\} = k/n \mid n_P(\mathcal{P}^R_{P_j}) = 0) \\
        &= \Pr(\min\{X_n^1, \dots, X_n^m\} = k/n).
    \end{align*}

    All that remains to show is that
    \begin{align*}
        \min\{X_n^1, \dots, X_n^m\} \xrightarrow[]{d} \min\{X^1, \dots, X^m\}.
    \end{align*}
    First, note that $(X_n^1, \dots, X_n^m) \xrightarrow[]{d} (X^1, \dots, X^m)$ due to the convergence of the marginal distributions and the fact that $X_n^j$ are independent.
    Furthermore, the mapping $x \mapsto \min\{x_1, \dots, x_m\}$ is continuous, and thus the continuous mapping theorem applies.

    Putting it all together, we have that
    \begin{align*}
        \varphi^{n, m}_P &= \sum_{k=0}^n \Pr(n_A(\mathcal{P}^R_{P_j}) \mid n_P(\mathcal{P}^R_{P_j}) = 0) f(k/n) \\
        &\xrightarrow[d]{} \sum_{k=0}^n \Pr(\min\{X_n^1, \dots, X_n^m\} = k/n) f(k/n) \\
        &= \E[\min\{X_n^1, \dots, X_n^m\}] \\
        &\to \E[\min\{X^1, \dots, X^m\}].
    \end{align*}
    If the cdf of $X^j$ is $G(t)$, then the cdf of $\min\{X^1, \dots, X^m\}$ is $1 - (1 - G(t))^m$, which concludes the proof.
\end{proof}

@@

\begin{proof}[Proof of Corollary \ref{cor:multiple_platforms_2}] (Assuming $f$ is continuously differentiable) %\textcolor{red}{(Assuming $f$ is continuously differentiable -- will have to relax this)}
    For any cdf $G$, the function $H(t) = 1 - [1 - G(t)]^m$ is increasing in $m$ for any $t$ unless $G(t) \equiv 0$ or $G(t) \equiv 1$.
    Therefore, the random variable with cdf $G$ first-order stochastically dominates the one with cdf $H$.
    As a result, the expected value of any monotonically increasing function is higher for the former than for the latter, unless the function is constant almost everywhere.
\end{proof}
